A sensor grid approach for large scale acoustic monitoring

### 2017-08-22 paper/article.tex
Paper corrections

%% \linenumbers
\clearpage
%% main text
\section{Introduction}
%\label{}
\pa{
// Beaucoup de fomer/latter
// Le terme soundscape inclut la perception de lenvironnment sonore. Si tu veux parler juste de lenvironnement sonore "urban sound environment" est plus approprie.
// Ref Judi: Picaut, Judicaël, Arnaud Can, Jérémy Ardouin, Pierre Crépeaux, Thierry Dhorne, David Écotière, Mathieu Lagrange, et al. « Characterization of urban sound environments using a comprehensive approach combining open data, measurements, and modeling ». In The Journal of the Acoustical Society of America, 141:3808-3808. Boston, USA: Acoustical Society of America, 2017. doi:10.1121/1.4988416.
}
The advent of low cost acoustic sensors together with the need to better monitor and comprehend the acoustic environment of urban and wilderness areas give rise to the deployment of experimental sensor networks such as the sonyc\footnote{\url{htttp://wp.nyu.edu/sonyc}} \cite{mydlarz2017implementation} and cense\footnote{\url{htttp://cense.ifsttar.fr}} \pa{ref papier de judicael ?} \cite{} projects.

@@

The measurement error is computed for third-octave bands. Results are displayed in Figure~\ref{fig:errorm}. Only full-octave bands are shown for visibility. When computing the slow analysis, we found that applying overlap attenuated the error. This was not observed for fast analysis where the error was similar or higher with the use of overlapping frames. We propose to study the absolute error metric, as all experiments show a mean error close to zero.

@@

\begin{figure*}[h!]
    \centering
    \begin{subfigure}[h]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{figures/err_m_n.eps}
        \caption{Noise extracts}
    \end{subfigure}
    \hfill
    \begin{subfigure}[h]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{figures/err_m_u.eps}
        \caption{Urban sounds recordings}
    \end{subfigure}

    \caption{Measurement error of third-octave bands over two-seconds recordings. The analysis of short frames has an effect on energy estimation at low frequencies. Framing is more impactful on signals where the energy is localized in frequency. \label{fig:errorm}}
\end{figure*}

>>>>

%% \linenumbers
\clearpage
%% main text
\section{Introduction}
%\label{}
\ac{-> Est-ce que le spectre est intelligible?
-> Reconnaissance?
-> Est-ce que envoyer le spectrogramme avec peu de bitrate?}
\pa{
// Beaucoup de fomer/latter
// Le terme soundscape inclut la perception de lenvironnment sonore. Si tu veux parler juste de lenvironnement sonore "urban sound environment" est plus approprie.
// Ref Judi: Picaut, Judicaël, Arnaud Can, Jérémy Ardouin, Pierre Crépeaux, Thierry Dhorne, David Écotière, Mathieu Lagrange, et al. « Characterization of urban sound environments using a comprehensive approach combining open data, measurements, and modeling ». In The Journal of the Acoustical Society of America, 141:3808-3808. Boston, USA: Acoustical Society of America, 2017. doi:10.1121/1.4988416.
}
The advent of low cost acoustic sensors together with the need to better monitor and comprehend the acoustic environment of urban and wilderness areas give rise to the deployment of experimental sensor networks such as the sonyc\footnote{\url{htttp://wp.nyu.edu/sonyc}} \cite{mydlarz2017implementation} and cense\footnote{\url{htttp://cense.ifsttar.fr}} \pa{ref papier de judicael ?} \cite{} projects.

@@

The measurement error is computed for third-octave bands. Results are displayed in Figure~\ref{fig:error_m}. Only full-octave bands are shown for visibility. When computing the slow analysis, we found that applying overlap attenuated the error. This was not observed for fast analysis where the error was similar or higher with the use of overlapping frames. We propose to study the absolute error metric, as all experiments show a mean error close to zero.

@@

\begin{figure*}[h!]
    \centering
    \begin{subfigure}[h]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{figures/err_m_n.eps} 
        \caption{Noise extracts}
    \end{subfigure}
    \hfill
    \begin{subfigure}[h]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{figures/err_m_u.eps} 
        \caption{Urban sounds recordings}
    \end{subfigure}
    \label{fig:error_m}
    \caption{Measurement error of third-octave bands over two-seconds recordings. The analysis of short frames has an effect on energy estimation at low frequencies. Framing is more impactful on signals where the energy is localized in frequency.}
\end{figure*}
